Author disambiguation of large-scale semi-labeled collections of scientific articles

### 2015-08-07 paper.tex
save

Author name disambiguation in bibliographic databases is the problem of
grouping together scientific publications written by a same person, accounting
for potential homonyms and/or synonyms. Among solutions to this problem,
digital libraries are increasingly offering tools for authors to manually
curate their publications and claim which ones are theirs. Indirectly, these
tools allow for the inexpensive collection of large annotated training data,
which can be further leveraged to build a complementary automated disambiguation system
capable of inferring patterns for identifying publications written by a same
person.  Building upon more than 1 million crowdsourced annotations, we
propose a automated author disambiguation solution exploiting this data (i) to learn
an accurate classifier for identifying corefering authors, (ii) to guide the
clustering of scientific publications by distinct authors in a semi-supervised
way and finally (iii) to match the resulting clusters with existing profiles.
To the best of our knowledge, our analysis is the first to be carried out on
data of this size and coverage. It reveals that... \glnote{To be completed with
actual results.}

>>>>

Author name disambiguation in bibliographic databases is the problem of
grouping together scientific publications written by a same person, accounting
for potential homonyms and/or synonyms. Among solutions to this problem,
digital libraries are increasingly offering tools for authors to manually
curate their publications and claim which ones are theirs. Indirectly, these
tools allow for the inexpensive collection of large annotated training data,
which can be further leveraged to build a complementary automated disambiguation system
capable of inferring patterns for identifying publications written by a same
person.  Building upon more than 1 million crowdsourced annotations, we
propose an automated author disambiguation solution exploiting this data (i) to learn
an accurate classifier for identifying corefering authors, (ii) to guide the
clustering of scientific publications by distinct authors in a semi-supervised
way and finally (iii) to match the resulting clusters with existing profiles.
To the best of our knowledge, our analysis is the first to be carried out on
data of this size and coverage. It reveals that... \glnote{To be completed with
actual results.}
